When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
put tcc rejection in crypto format

\documentclass{llncs}
% \documentclass{llncs}
\def\shownotes{1}
\def\blinded{1}

%\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

@@

\begin{lemma}
\label{lem:fuzz can't get key}
Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
\end{lemma}
\begin{proof}
As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
\[
(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
\]
%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

>>>>

\def\shownotes{0}
\def\blinded{1}
\def\lncs{1}

\ifnum\lncs=0
	\documentclass[11pt]{article}
	\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
	\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
	%\geometry{landscape}                % Activate for for rotated page geometry
	%\usepackage[parfill]{parskip}
	\usepackage{amsthm}
	\newtheorem{theorem}{Theorem}[section]
	\newtheorem{lemma}[theorem]{Lemma}
	\newtheorem{proposition}[theorem]{Proposition}
	\newtheorem{corollary}[theorem]{Corollary}
	\newtheorem{definition}[theorem]{Definition}
	\newtheorem{assumption}[theorem]{Assumption}
	\newtheorem{claim}[theorem]{Claim}
	\newtheorem{problem}[theorem]{Problem}
	\newtheorem{construction}[theorem]{Construction}

\else
	\documentclass[runningheads]{llncs}
	\newtheorem{construction}{Construction}
\fi

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{construction}[theorem]{Construction}

@@

\begin{lemma}
\label{lem:fuzz can't get key}
Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
\end{lemma}
\begin{proof}
As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
\[
(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
\]
%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]
